# 1 Exercise

## Current protocol

### EWOT

EWOT or Exercise With Oxygen Therapy is a powerful modality. Here is what I'm doing.

There are two separate workouts that are done on alternating days, six days a week.

```{r}
library(gt)
library(dplyr)


workout_data <- tibble(
    Week = c(
    1,2,3,4
  ),
  Warmup = "5min",
  
  'Low 02' = c(
    "1min", "2min", "3min", "4min"
  ),
  'High O2' = c(
    "4min", "3min", "2min", "1min"
  )
)

# Create the gt table with grouping
workout_table <- workout_data %>%
  gt() %>%
  tab_header(
    title = "Contrast EWOT Workout",
    subtitle = "Performed 4x/week"
  ) %>%
gt::tab_spanner(
    label = "3 Sets*",
    columns = c(`Low 02`, `High O2`)
  ) |>
    tab_source_note("* Perform the Low O2 then High O2 sections = 1 set. Do that 3x") |>

  tab_options(
       table.width = pct(100),
    heading.title.font.size = px(24),
    heading.subtitle.font.size = px(16),
    heading.title.font.weight = "bold",
    heading.background.color = "#ddedff",
    column_labels.font.weight = "bold",
      table.background.color = "#ddedff",
    row_group.background.color = "#b3b3b3",
    row_group.font.weight = "bold",
    table.border.top.style = "none",
    table.border.bottom.style = "none"
  ) 


# Display the table
workout_table
```

```{r}
workout_data <- tibble(
  Section = c(
    "1. WARMUP",
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)", 
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)", 
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)"
  ),
  Activity = c(
    "Easy warmup",
    "Sprint Interval",
    "Rest Interval",
    "Repeat"
  ),
  Instructions = c(
    "Moderate activity with oxygen",
    "80-95% effort with oxygen",
    "Light recovery effort with oxygen",
    "Perform 4 sets"
  ),
  Duration = c(
    "10 minutes",
    "4 minutes",
    "3 minutes",
    "-"
  ),
  Intensity = c(
    "Low (40-50%)",
    "High (80-95% max)",
    "Low (40-50%)",
    "-"
  )
)

# Create the gt table with grouping
workout_table <- workout_data %>%
  gt(groupname_col = "Section") %>%
  tab_header(
    title = "Norweigan 4x4",
    subtitle = "Performed 2x/week"
  ) %>%
  fmt_markdown(columns = c(Instructions)) %>%
  tab_style(
    style = cell_fill(color = "#e6f2ff"),
    locations = cells_body(rows = 1)
  ) %>%
  tab_style(
    style = cell_fill(color = "#ffecec"),
    locations = cells_body(rows = 2)
  ) %>%
  tab_style(
    style = cell_fill(color = "#f0f0f0"),
    locations = cells_body(rows = 4)
  ) %>%
  tab_style(
    style = cell_fill(color = "#fff2cc"),
    locations = cells_body(rows = 3)
  ) %>%
  # tab_style(
  #   style = cell_fill(color = "#e6f2ff"),
  #   locations = cells_body(rows = 7)
  # ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "#d9d9d9")
    ),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", size = px(14)),
      cell_fill(color = "#b3b3b3")
    ),
    locations = cells_row_groups()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = Activity)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", color = "#cc0000"),
    locations = cells_body(columns = Intensity, rows = 2)
  ) %>%
  # tab_style(
  #   style = list(
  #     cell_borders(
  #       sides = "all",
  #       color = "gray",
  #       weight = px(1)
  #     )
  #   ),
  #   locations = cells_body()
  # ) %>%
  tab_options(
    table.width = pct(100),
    heading.title.font.size = px(24),
    heading.subtitle.font.size = px(16),
    heading.title.font.weight = "bold",
    heading.background.color = "#ddedff",
    
    column_labels.font.weight = "bold",
    row_group.background.color = "#b3b3b3",
    row_group.font.weight = "bold",
    table.border.top.style = "none",
    table.border.bottom.style = "none"
  ) 
     # gtExtras::gt_theme_nytimes()

# Display the table
workout_table
```

## Past protocols

<details>

<summary>March - May 2025</summary>

### EWOT

EWOT or Exercise With Oxygen Therapy is a powerful modality. Here is what I'm doing.

There are two separate workouts that are done on alternating days, seven days a week.

#### Workout A:

```{r}
library(gt)
library(dplyr)


workout_data <- tibble(
  Section = c(
    "1. WARMUP", "1. WARMUP",
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)", 
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)", 
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)",
    "2. SPRINT CLUSTERS (Repeat 3-5 clusters)",
    "3. STEADY STATE"
  ),
  Activity = c(
    "Without Oxygen", "With Oxygen",
    "Sprint Interval", "Rest Interval", "Repeat", "Recovery Between Clusters",
    "Calorie Target"
  ),
  Instructions = c(
    "Moderate activity", "Moderate activity with oxygen",
    "All-out maximum effort", "Complete rest", "Repeat sprint/rest intervals 3-5 times to complete one cluster", "Moderate pace after completing each cluster",
    "Continue at normal steady state"
  ),
  Duration = c(
    "2 minutes", "2 minutes",
    "20 seconds", "10 seconds", "~2.5 minutes per complete cluster", "2 minutes",
    "Until reaching 500 calories"
  ),
  Intensity = c(
    "Low (40-50%)", "Low (40-50%)",
    "Maximum (100%)", "None (0%)", "Alternating", "Moderate (40-60%)",
    "Moderate (60-70%)"
  )
)

# Create the gt table with grouping
workout_table <- workout_data %>%
  gt(groupname_col = "Section") %>%
  tab_header(
    title = "Tabata EWOT Workout A",
    subtitle = "High-Intensity Interval Training with Oxygen Protocol"
  ) %>%
  fmt_markdown(columns = c(Instructions)) %>%
  tab_style(
    style = cell_fill(color = "#e6f2ff"),
    locations = cells_body(rows = 1:2)
  ) %>%
  tab_style(
    style = cell_fill(color = "#ffecec"),
    locations = cells_body(rows = 3)
  ) %>%
  tab_style(
    style = cell_fill(color = "#f0f0f0"),
    locations = cells_body(rows = 4)
  ) %>%
  tab_style(
    style = cell_fill(color = "#fff2cc"),
    locations = cells_body(rows = 5:6)
  ) %>%
  tab_style(
    style = cell_fill(color = "#e6f2ff"),
    locations = cells_body(rows = 7)
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "#d9d9d9")
    ),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", size = px(14)),
      cell_fill(color = "#b3b3b3")
    ),
    locations = cells_row_groups()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = Activity)
  ) %>%
  tab_style(
    style = cell_text(weight = "bold", color = "#cc0000"),
    locations = cells_body(columns = Intensity, rows = 3)
  ) %>%
  # tab_style(
  #   style = list(
  #     cell_borders(
  #       sides = "all",
  #       color = "gray",
  #       weight = px(1)
  #     )
  #   ),
  #   locations = cells_body()
  # ) %>%
  tab_options(
    table.width = pct(100),
    heading.title.font.size = px(24),
    heading.subtitle.font.size = px(16),
    heading.title.font.weight = "bold",
    heading.background.color = "#ddedff",
    column_labels.font.weight = "bold",
    row_group.background.color = "#b3b3b3",
    row_group.font.weight = "bold",
    table.border.top.style = "none",
    table.border.bottom.style = "none"
  ) |>
     gtExtras::gt_theme_nytimes()

# Display the table
workout_table
```

This workout is tough. Use contrast as well (breath low-oxygen during sprints).

#### Workout B:

```{r}

# Create data frame for the workout with better structure
workout_data <- tibble(
  Section = c(
    "1. WARMUP",
    "2. STEADY STATE"
  ),
  Activity = c(
    "With Oxygen", "With Oxygen"
  ),
  Instructions = c(
    "Moderate activity with oxygen", "Moderate - Heavy activity with oxygen"
  ),
  Duration = c(
    "2 minutes", "Until reaching 500 - 1,000 calories"
  ),
  Intensity = c(
    "Low (40-50%)", "Moderate (40-60%)"
  )
)

# Create the gt table with grouping
workout_table_b <- workout_data %>%
  gt(groupname_col = "Section") %>%
  tab_header(
    title = "Steady State EWOT Workout B",
    subtitle = "Steady State Training with Oxygen Protocol"
  ) %>%
  fmt_markdown(columns = c(Instructions)) %>%
  tab_style(
    style = cell_fill(color = "#e6f2ff"),
    locations = cells_body(rows = 1)
  ) %>%
  tab_style(
    style = cell_fill(color = "#fff2cc"),
    locations = cells_body(rows = 2)
  ) %>%
  # tab_style(
  #   style = cell_fill(color = "#f0f0f0"),
  #   locations = cells_body(rows = 4)
  # ) %>%
  # tab_style(
  #   style = cell_fill(color = "#fff2cc"),
  #   locations = cells_body(rows = 5:6)
  # ) %>%
  # tab_style(
  #   style = cell_fill(color = "#e6f2ff"),
  #   locations = cells_body(rows = 7)
  # ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold"),
      cell_fill(color = "#d9d9d9")
    ),
    locations = cells_column_labels()
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold", size = px(14)),
      cell_fill(color = "#b3b3b3")
    ),
    locations = cells_row_groups()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(columns = Activity)
  ) %>%
  # tab_style(
  #   style = cell_text(weight = "bold", color = "#cc0000"),
  #   locations = cells_body(columns = Intensity, rows = 3)
  # ) %>%
  # tab_style(
  #   style = list(
  #     cell_borders(
  #       sides = "all",
  #       color = "gray",
  #       weight = px(1)
  #     )
  #   ),
  #   locations = cells_body()
  # ) %>%
  tab_options(
    table.width = pct(100),
    heading.title.font.size = px(24),
    heading.subtitle.font.size = px(16),
    heading.title.font.weight = "bold",
    heading.background.color = "#ddedff",
    column_labels.font.weight = "bold",
    row_group.background.color = "#b3b3b3",
    row_group.font.weight = "bold",
    table.border.top.style = "none",
    table.border.bottom.style = "none"
  ) |>
     gtExtras::gt_theme_nytimes()

# Display the table
workout_table_b
```

Also use contrast here, alternating low oxygen with high.

</details>